Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber}}

### 2019-05-31 Paper.tex
Update Paper.tex

For most functions, an uppercase letter is used, e.g. $C$, the general cost function. These may be subscripted to denote specialised variants, \eg \hyperlink{C__SSTORE}{$C_\text{SSTORE}$}, the cost function for the \hyperlink{SSTORE}{{\tiny SSTORE}} operation. For specialised and possibly externally defined functions, we may format as typewriter text, \eg the Keccak-256 hash function (as per version 3 of the winning entry to the SHA-3 contest by \cite{Keccak}, rather than the final SHA-3 specification), is denoted $\texttt{KEC}$ (and generally referred to as plain Keccak). Also, $\texttt{KEC512}$ refers to the Keccak-512 hash function.

@@

We define a precompiled contract for scalar multiplication on $G_1$, where $\bar I_{\mathbf{d}}$ is defined in (\ref{eq:complemented_input}).
\begin{eqnarray}
\Xi_{\mathtt{BN\_MUL}}&\equiv&\Xi_{\mathtt{PRE}}\quad\text{except:}\\
\Xi_{\mathtt{BN\_MUL}}(\boldsymbol\sigma,g,I)&=&\left(\varnothing,0,A^0,()\right)\quad\text{if}\ x=\varnothing\\
g_{\mathrm{r}} &=& 40000\\
\mathbf{o}&\equiv&\delta_1^{-1}(n\cdot x)\quad\text{where $\cdot$ is the scalar multiplication in $G_1$}\\
x&\equiv&\delta_1\left(\bar I_{\mathbf{d}}[0..63]\right)\\
n&\equiv&\bar I_{\mathbf{d}}[64..95]
\end{eqnarray}

>>>>

For most functions, an uppercase letter is used, e.g. $C$, the general cost function. These may be subscripted to denote specialised variants, \eg \hyperlink{C__SSTORE}{$C_\text{SSTORE}$}, the cost function for the \hyperlink{SSTORE}{{\tiny SSTORE}} operation. For specialised and possibly externally defined functions, we may format as typewriter text, \eg the Keccak-256 hash function (as per the winning entry to the SHA-3 contest by \cite{Keccak}, rather than later releases), is denoted $\texttt{KEC}$ (and generally referred to as plain Keccak). Also $\texttt{KEC512}$ is referring to the Keccak 512 hash function.

@@

We define a precompiled contract for scalar multiplication on $G_1$, where $\bar I_{\mathbf{d}}$ is defined in (\ref{eq:complemented_input}).
\begin{eqnarray}
\Xi_{\mathtt{BN\_MUL}}&\equiv&\Xi_{\mathtt{PRE}}\quad\text{except:}\\
\Xi_{\mathtt{BN\_MUL}}(\boldsymbol\sigma,g,I)&=&\left(\varnothing,0,A^0,()\right)\quad\text{if}\ x=\varnothing\\
g_{\mathrm{r}} &=& 40000\\
\mathbf{o}&\equiv&\delta_1^{-1}(n\cdot x)\quad\text{where $\cdot$ is the scalar multiplication in $G_1$}\\
n&\equiv&\bar I_{\mathbf{d}}[0..31]\\
x&\equiv&\delta_1\left(\bar I_{\mathbf{d}}[32..95]\right)
\end{eqnarray}
